---
title: "dashboard_1"
author: "Vasili Fokaidis"
output: 
  flexdashboard::flex_dashboard:
    orientation: columns
    vertical_layout: fill
    source: embed
---

```{r}
library(tidyverse)
library(gganimate)

knitr::opts_chunk$set(
	echo = TRUE,
	warning = FALSE,
	fig.width = 8, 
  fig.height = 6,
  out.width = "90%"
)

theme_set(theme_minimal() + theme(legend.position = "bottom"))

options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

Read in acs race data and acs hispanic data. And manipulate respective data to make scatter plots.

```{r}
race_df = 
  read_csv("ACS_data/ACS_2017_race.csv") %>%
  rename(
    total = "K200201_001E",
    white = "K200201_002E",
    black = "K200201_003E",
    am_ind_al_nat = "K200201_004E",
    asian = "K200201_005E",
    nat_ha_pac_isl = "K200201_006E",
    other = "K200201_007E",
    two_or_more = "K200201_008E",
    county_state = "NAME"
  ) %>%
  janitor::clean_names() %>%
  select(geo_id, county_state, total, white, black, am_ind_al_nat, asian, nat_ha_pac_isl, other, two_or_more) %>%
  slice(-1) %>%
  mutate(
    total = as.numeric(total),
    white = as.numeric(white),
    black = as.numeric(black),
    am_ind_al_nat = as.numeric(am_ind_al_nat),
    asian = as.numeric(asian),
    nat_ha_pac_isl = as.numeric(nat_ha_pac_isl), 
    other = as.numeric(other),
    two_or_more = as.numeric(two_or_more)
  )

hispanic_df = 
  read_csv("ACS_data/ACS_2017_hispanic.csv") %>%
   rename(
    total = "K200301_001E",
    hispanic = "K200301_003E",
    county_state = "NAME"
  ) %>%
  janitor::clean_names() %>%
  select(geo_id, county_state, total, hispanic) %>%
  slice(-1) %>%
  mutate(
    total = as.numeric(total),
    hispanic = as.numeric(hispanic)
  )


  
```

Percent function, and percents of each race by county.

```{r}
per_f = function(x) {

  x/race_df$total * 100
  
}

per_f_h = function(y) {
  
  y/hispanic_df$total * 100
  
}

race_df = 
  race_df %>%
  mutate(
    white = per_f(white),
    black = per_f(black),
    am_ind_al_nat = per_f(am_ind_al_nat),
    asian = per_f(asian),
    nat_ha_pac_isl = per_f(nat_ha_pac_isl),
    other = per_f(other),
    two_or_more = per_f(two_or_more)
  )

hispanic_df = 
  hispanic_df %>%
  mutate(
    hispanic = per_f_h(hispanic)
  ) %>%
  select(geo_id, hispanic)

race_hisp_df =
  inner_join(x = race_df, y = hispanic_df, by = "geo_id", all = TRUE)
```

Read in 2017 mtm data, and merge with acs race data.

```{r}
mtm_2017 = 
  read_csv("mtm_acs_2017_df.csv") %>%
  rename(
    geo_id = id
  )

mtm_2017_acs_2017_race_df = 
  inner_join(x = race_hisp_df, y = mtm_2017, by = "geo_id", all = TRUE)
```

Making transitioning graph for food insecurity by percent of race in each county across the U.S.

```{r}
race_per_plot =
  
mtm_2017_acs_2017_race_df %>%
  pivot_longer(
    white:hispanic,
    names_to = "race",
    values_to = "percents"
  ) %>%
  mutate(
    race = str_replace(race, "white", "White"),
    race = str_replace(race, "black", "Black"),
    race = str_replace(race, "am_ind_al_nat", "American Indian and Alaska Native"),
    race = str_replace(race, "asian", "Asian"),
    race = str_replace(race, "nat_ha_pac_isl", "Native Hawaiian and Other Pacific Islander"),
    race = str_replace(race, "other", "Other Race"),
    race = str_replace(race, "two_or_more", "Two or More Races"),
    race = str_replace(race, "hispanic", "Hispanic")
    ) %>%
  select(geo_id, total, race, percents, fi_rate) %>%
  drop_na() %>%
  ggplot(aes(x = fi_rate, y = percents, size = total, color = race)) + 
  geom_point(show.legend = FALSE, alpha = 0.8) +
  labs(
    title = '{closest_state}',
    x = "Food Insecurity Rate",
    y = "% Race Within Each County"
  ) +
  theme_bw() +
  transition_states(race, transition_length = 1, state_length = 3, wrap = TRUE) + 
  enter_fade() + 
  exit_fade() +
  ease_aes('cubic-in-out')

animate(race_per_plot, fps = 5, height = 500, width = 1000)
```

Read in education attainment acs data.

```{r}
edu_att = 
  read_csv("ACS_data/ACS_2017_edu.csv") %>%
   rename(
    total = "K201501_001E",
    less_9th = "K201501_002E",
    nineth_to_12th = "K201501_003E",
    hs_grad = "K201501_004E",
    some_coll = "K201501_005E",
    assoc_deg = "K201501_006E",
    bach_deg = "K201501_007E",
    grad_or_prof = "K201501_008E",
    county_state = "NAME"
  ) %>%
  janitor::clean_names() %>%
  select(geo_id, total, less_9th, nineth_to_12th, hs_grad, some_coll, assoc_deg, bach_deg, grad_or_prof) %>%
  slice(-1) %>%
  mutate(
    total = as.numeric(total),
    less_9th = as.numeric(less_9th),
    nineth_to_12th = as.numeric(nineth_to_12th),
    hs_grad = as.numeric(hs_grad),
    some_coll = as.numeric(some_coll),
    assoc_deg = as.numeric(assoc_deg),
    bach_deg = as.numeric(bach_deg),
    grad_or_prof = as.numeric(grad_or_prof))
```

Percent function, and percents for education attainment % by county.

```{r}
per_f_edu = function(x) {

  x/edu_att$total * 100
  
}

edu_att = 
  edu_att %>%
  mutate(
    less_9th = per_f_edu(less_9th),
    nineth_to_12th = per_f_edu(nineth_to_12th),
    hs_grad = per_f_edu(hs_grad),
    some_coll = per_f_edu(some_coll),
    assoc_deg = per_f_edu(assoc_deg),
    bach_deg = per_f_edu(bach_deg),
    grad_or_prof = per_f_edu(grad_or_prof)
  )

```

Merge with acs education data.

```{r}
mtm_2017_edu_2017_att_df =
  inner_join(x = edu_att, y = mtm_2017, by = "geo_id", all = TRUE)
```

Making transitioning graph for food insecurity by percent of education attainment category in each county across the U.S.

```{r}
edu_per_plot =
  
mtm_2017_edu_2017_att_df %>%
  pivot_longer(
    less_9th:grad_or_prof,
    names_to = "edu_att",
    values_to = "percents"
  ) %>%
  mutate(
    edu_att = str_replace(edu_att, "less_9th", "Less Than 9th Grade"),
    edu_att = str_replace(edu_att, "nineth_to_12th", "9th to 12th Grade"),
    edu_att = str_replace(edu_att, "hs_grad", "High School Graduate"),
    edu_att = str_replace(edu_att, "some_coll", "Some College"),
    edu_att = str_replace(edu_att, "assoc_deg", "Associate's Degree"),
    edu_att = str_replace(edu_att, "bach_deg", "Bachelor's Degree"),
    edu_att = str_replace(edu_att, "grad_or_prof", "Graduate or Professional Degree")
    ) %>%
  select(geo_id, total, edu_att, percents, fi_rate) %>%
  drop_na() %>%
  ggplot(aes(x = fi_rate, y = percents, size = total, color = edu_att)) + 
  geom_point(show.legend = FALSE, alpha = 0.8) +
  labs(
    title = '{closest_state}',
    x = "Food Insecurity Rate",
    y = "% Education Attainment Within Each County"
  ) +
  theme_bw() +
  transition_states(edu_att, transition_length = 1, state_length = 3, wrap = TRUE) + 
  enter_fade() + 
  exit_fade() +
  ease_aes('cubic-in-out')

animate(edu_per_plot, fps = 5, height = 500, width = 1000)
```