---
title: "interactive_plot_demographics"
author: "Stella Li"
date: "11/25/2020"
output: html_document
runtime: shiny
---

```{r import libraries}
library(tidyverse)
library(plotly)
library(rjson)
library(rvest)
library(httr)
library(usdata)
library(shiny)
```



```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r eruptions, echo=FALSE}
inputPanel(
  selectInput("n_breaks", label = "Number of bins:",
              choices = c(10, 20, 35, 50), selected = 20),
  
  sliderInput("bw_adjust", label = "Bandwidth adjustment:",
              min = 0.2, max = 2, value = 1, step = 0.2)
)

renderPlot({
  hist(faithful$eruptions, probability = TRUE, breaks = as.numeric(input$n_breaks),
       xlab = "Duration (minutes)", main = "Geyser eruption duration")
  
  dens <- density(faithful$eruptions, adjust = input$bw_adjust)
  lines(dens, col = "blue")
})
```

## Embedded Application

It's also possible to embed an entire Shiny application within an R Markdown document using the `shinyAppDir` function. This example embeds a Shiny application located in another directory:

```{r tabsets, echo=FALSE}
shinyAppDir(
  system.file("examples/06_tabsets", package = "shiny"),
  options = list(
    width = "100%", height = 550
  )
)
```

Note the use of the `height` parameter to determine how much vertical space the embedded application should occupy.

You can also use the `shinyApp` function to define an application inline rather then in an external directory.

In all of R code chunks above the `echo = FALSE` attribute is used. This is to prevent the R code within the chunk from rendering in the document alongside the Shiny components.

Import FIPS data (https://mdreducation.com/ >pdfs > US_FIPS_Codes), tidy it and join it to the map the meal gap data.
```{r fips data}
fips_df = readxl::read_xls("./fips_data/US_FIPS_Codes.xls", skip = 1) %>%
  janitor::clean_names() %>%
  rename(county = county_name) %>%
  unite("fips", c("fips_state", "fips_county"), sep = "") %>%
  mutate(county = tolower(county),
         state = state2abbr(state),
         county = str_replace(county, ",.*", ""),
         county = str_replace(county, "\\scounty",""),
         county = str_replace(county, "\\sparish",""),
         county = str_replace(county, "\\sborough", ""),
         county = str_replace(county, "\\scensus area", ""),
         county = str_replace(county, "\\smunicipality of", ""),
         county = str_replace(county, "dona ana", "doña ana"),
         county = str_replace(county, "^st\\s|^st\\.", "saint "),
         county = str_replace(county, "de kalb", "dekalb")
  ) %>%
unite("county_state", c("county", "state"), sep = "_", remove = FALSE) %>%
  mutate(county_state = str_replace(county_state, "prince of wales-outer ketchikan_AK", "prince of wales-hyder_AK"),
         county_state = str_replace(county_state, "matanuska susitna_AK", "matanuska-susitna_AK"),
         county_state = str_replace(county_state, "valdez cordova_AK", "valdez-cordova_AK"),
         county_state = str_replace(county_state, "juneau_AK", "city and of juneau_AK"),
         county_state = str_replace(county_state, "dekalb_TN", "de kalb_TN"),
         county_state = str_replace(county_state, "dekalb_IN", "de kalb_IN"),
         county_state = str_replace(county_state, "dewitt_IL", "de witt_IL"),
         county_state = str_replace(county_state, "de soto_MS", "desoto_MS"),
         county_state = str_replace(county_state, "de soto_FL", "desoto_FL"),
         county_state = str_replace(county_state, "du page_IL", "dupage_IL"),
         county_state = str_replace(county_state, "skagway hoonah angoon_AK", "hoonah-angoon_AK"),
         county_state = str_replace(county_state, "skagway hoonah angoon_AK", "hoonah-angoon_AK"),
         county_state = str_replace(county_state, "wrangell petersburg_AK", "petersburg_AK"),
         county_state = str_replace(county_state, "prince georges_MD", "prince george's_MD"),
         county_state = str_replace(county_state, "prince wales ketchikan_AK", "prince of wales-hyder_AK")
) %>%
  select(county_state, fips)


map_the_meal_gap_df = read_csv("./map_the_meal_gap_df.csv")

mtm_fips_df = left_join(map_the_meal_gap_df, fips_df, by = "county_state")

new_DF <- mtm_fips_df[is.na(mtm_fips_df$fips),]

```







```{r plot attempt}
url <- 'https://raw.githubusercontent.com/plotly/datasets/master/geojson-counties-fips.json'
counties <- rjson::fromJSON(file=url)
url2<- "https://raw.githubusercontent.com/plotly/datasets/master/fips-unemp-16.csv"
df <- read.csv(url2, colClasses=c(fips="character"))
g <- list(
  scope = 'usa',
  projection = list(type = 'albers usa'),
  showlakes = TRUE,
  lakecolor = toRGB('white')
)
fig <- plot_ly()
fig <- fig %>% add_trace(
    type="choropleth",
    geojson=counties,
    locations=df$fips,
    z=df$unemp,
    colorscale="Viridis",
    zmin=0,
    zmax=12,
    marker=list(line=list(
      width=0)
    )
  )
fig <- fig %>% colorbar(title = "Unemployment Rate (%)")
fig <- fig %>% layout(
    title = "2016 US Unemployment by County"
)

fig <- fig %>% layout(
    geo = g
  )

fig
```
















